---
title: "Coronavirus India & US Dashboard"
author: "by Mithun Ghosh"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    # social: ["facebook", "twitter", "linkedin"]
    source_code: embed
    vertical_layout: fill
---

```{r setup, include=FALSE}
#------------------ Packages ------------------
library(flexdashboard)
# install.packages("devtools")
# devtools::install_github("RamiKrispin/coronavirus", force = TRUE)
#library(coronavirus)
#data(coronavirus)
#update_datasets()
# View(coronavirus)
# max(coronavirus$date)
coronavirus <- read.csv(file="https://raw.githubusercontent.com/RamiKrispin/coronavirus/master/csv/coronavirus.csv",header=TRUE,sep=",")

`%>%` <- magrittr::`%>%`
#------------------ Parameters ------------------
# Set colors
# https://www.w3.org/TR/css-color-3/#svg-color
confirmed_color <- "purple"
active_color <- "#1f77b4"
recovered_color <- "forestgreen"
death_color <- "red"
#------------------ Data ------------------
df <- coronavirus %>%
  # dplyr::filter(date == max(date)) %>%
  dplyr::filter(country == "India") %>%
  dplyr::group_by(country, type) %>%
  dplyr::summarise(total = sum(cases)) %>%
  tidyr::pivot_wider(
    names_from = type,
    values_from = total
  ) %>%
  # dplyr::mutate(unrecovered = confirmed - ifelse(is.na(recovered), 0, recovered) - ifelse(is.na(death), 0, death)) %>%
  dplyr::mutate(unrecovered = confirmed - ifelse(is.na(death), 0, death) -ifelse(is.na(recovered), 0, recovered) ) %>%
  dplyr::arrange(-confirmed) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(country = dplyr::if_else(country == "United Arab Emirates", "UAE", as.character(country))) %>%
  dplyr::mutate(country = dplyr::if_else(country == "Mainland China", "China", country)) %>%
  dplyr::mutate(country = dplyr::if_else(country == "North Macedonia", "N.Macedonia", country)) %>%
  dplyr::mutate(country = trimws(country)) %>%
  dplyr::mutate(country = factor(country, levels = country))

df_daily <- coronavirus %>%
  dplyr::filter(country == "India") %>%
  dplyr::group_by(date, type) %>%
  dplyr::summarise(total = sum(cases, na.rm = TRUE)) %>%
  tidyr::pivot_wider(
    names_from = type,
    values_from = total
  ) %>%
  dplyr::arrange(date) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(active = confirmed - death -recovered) %>%
  dplyr::mutate(
    confirmed_cum = cumsum(confirmed),
    death_cum = cumsum(death),
    recovered_cum = cumsum(recovered),
    active_cum = cumsum(active)
  )

df_daily_us <- coronavirus %>%
  dplyr::filter(country == "US") %>%
  dplyr::group_by(date, type) %>%
  dplyr::summarise(total = sum(cases, na.rm = TRUE)) %>%
  tidyr::pivot_wider(
    names_from = type,
    values_from = total
  ) %>%
  dplyr::arrange(date) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(active = confirmed - death -recovered) %>%
  dplyr::mutate(
    confirmed_cum = cumsum(confirmed),
    death_cum = cumsum(death),
    recovered_cum = cumsum(recovered),
    active_cum = cumsum(active)
  )

df1 <- coronavirus %>% dplyr::filter(date == max(as.character(date)))
```

Summary for India
=======================================================================

Row {data-width=400}
-----------------------------------------------------------------------

### confirmed {.value-box}

```{r}

valueBox(
  value = paste(format(sum(df$confirmed), big.mark = ","), "", sep = " "),
  caption = "Total confirmed cases",
  icon = "fas fa-user-md",
  color = confirmed_color
)
```


### active {.value-box}
```{r}
 valueBox( 
   value = paste(format(sum(df$unrecovered, na.rm = TRUE), big.mark = ","), " (",
     round(100 * sum(df$unrecovered, na.rm = TRUE) / sum(df$confirmed), 1),
     "%)",
     sep = "" 
   ),
   caption = "Active cases (% of total cases)", icon = "fas fa-ambulance",
   color = active_color
 ) 
``` 

### death {.value-box}

```{r}

valueBox(
  value = paste(format(sum(df$death, na.rm = TRUE), big.mark = ","), " (",
    round(100 * sum(df$death, na.rm = TRUE) / sum(df$confirmed), 1),
    "%)",
    sep = ""
  ),
  caption = "Death cases (death rate)",
  icon = "fas fa-heart-broken",
  color = death_color
)
```


Row
-----------------------------------------------------------------------

### **Daily cumulative cases by type** (India only)

```{r}
df_daily <- df_daily %>% dplyr::filter(as.character(date) > "2020-01-31") 
plotly::plot_ly(data = df_daily) %>%
  plotly::add_trace(
    x = ~date,
    # y = ~active_cum,
    y = ~confirmed_cum,
    type = "scatter",
    mode = "lines+markers",
    # name = "Active",
    name = "Confirmed",
    line = list(color = confirmed_color),
    marker = list(color = confirmed_color)
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~ confirmed_cum - recovered_cum - death_cum,
    type = "scatter",
    mode = "lines+markers",
    name = "Active Cases",
    line = list(color = active_color),
    marker = list(color = active_color)
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~ recovered_cum,
    type = "scatter",
    mode = "lines+markers",
    name = "Recovered",
    line = list(color = recovered_color),
    marker = list(color = recovered_color)
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~death_cum,
    type = "scatter",
    mode = "lines+markers",
    name = "Death",
    line = list(color = death_color),
    marker = list(color = death_color)
  ) %>%
  plotly::add_annotations(
    x = as.Date("2020-01-31"),
    y = 1,
    text = paste("First case"),
    xref = "x",
    yref = "y",
    arrowhead = 5,
    arrowhead = 3,
    arrowsize = 1,
    showarrow = TRUE,
    ax = -10,
    ay = -90
  ) %>%
  plotly::add_annotations(
    x = as.Date("2020-03-12"),
    y = 3,
    text = paste("First death"),
    xref = "x",
    yref = "y",
    arrowhead = 5,
    arrowhead = 3,
    arrowsize = 1,
    showarrow = TRUE,
    ax = -90,
    ay = -90
  ) %>%
  plotly::add_annotations(
    x = as.Date("2020-03-22"),
    y = 14,
    text = paste(
      "New containment",
      "<br>",
      "measures"
    ),
    xref = "x",
    yref = "y",
    arrowhead = 5,
    arrowhead = 3,
    arrowsize = 1,
    showarrow = TRUE,
    ax = -10,
    ay = -90
  ) %>%
  plotly::layout(
    title = "",
    yaxis = list(title = "Cumulative number of cases"),
    xaxis = list(title = "Date"),
    legend = list(x = 0.1, y = 0.9),
    hovermode = "compare"
  )
```
Row
-----------------------------------------------------------------------

### **Daily cumulative cases by type Log10 Scale** (India only)

```{r}
plotly::plot_ly(data = df_daily) %>%
  plotly::add_trace(
    x = ~date,
    # y = ~active_cum,
    y = ~log10(confirmed_cum),
    type = "scatter",
    mode = "lines+markers",
    # name = "Active",
    name = "Confirmed",
    line = list(color = confirmed_color),
    marker = list(color = confirmed_color)
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~ log10(confirmed_cum - recovered_cum - death_cum),
    type = "scatter",
    mode = "lines+markers",
    name = "Active Cases",
    line = list(color = active_color),
    marker = list(color = active_color)
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~ log10(recovered_cum),
    type = "scatter",
    mode = "lines+markers",
    name = "Recovered",
    line = list(color = recovered_color),
    marker = list(color = recovered_color)
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~log10(death_cum),
    type = "scatter",
    mode = "lines+markers",
    name = "Death",
    line = list(color = death_color),
    marker = list(color = death_color)
  ) %>%
  plotly::layout(
    title = "",
    yaxis = list(title = "Cumulative number of cases"),
    xaxis = list(title = "Date"),
    legend = list(x = 0.1, y = 0.9),
    hovermode = "compare"
  )
```

Comparison
=========================================================================================

Column
-------------------------------------------------------------------------------

### ** Daily Growth Rate of Total Cases from March (India Only)**

```{r}
df_april <- df_daily %>% dplyr::filter(as.character(date) > "2020-03-06")  %>% dplyr::mutate(total_case_growth = confirmed_cum / dplyr::lag(confirmed_cum,k=1)) %>%
dplyr::mutate(active_case_growth = active_cum / dplyr::lag(active_cum,k=1)) %>%
dplyr::mutate(death_case_growth = death_cum / dplyr::lag(death_cum,k=1)) 
plotly::plot_ly(data = df_april) %>%
  plotly::add_trace(
    x = ~date,
    y = ~ total_case_growth - 1,
    type = "scatter",
    mode = "lines+markers",
    name = " Daily Growth Rate of Total Cases",
    line = list(color = active_color),
    marker = list(color = active_color)
  ) %>%
    plotly::add_trace(
    x = ~date,
    y = ~ active_case_growth - 1,
    type = "scatter",
    mode = "lines+markers",
    name = " Daily Growth Rate of Active Cases",
    line = list(color = recovered_color),
    marker = list(color = recovered_color)
  ) %>%
  #  plotly::add_trace(
  #   x = ~date,
  #   y = ~ death_case_growth - 1,
  #   type = "scatter",
  #   mode = "lines+markers",
  #   name = " Daily Growth Rate of Death Cases",
  #   line = list(color = death_color),
  #   marker = list(color = death_color)
  # ) %>%
  plotly::layout(
    title = "",
    legend = list(x = 0.1, y = 0.9),
    yaxis = list(title = "Daily Growth Rate"),
    xaxis = list(title = "Date")
  )
```



### ** Daily Growth Rate of Total Cases from March (US Only)**

```{r}
df_april <- df_daily_us %>% dplyr::filter(as.character(date) > "2020-03-06")  %>% dplyr::mutate(total_case_growth = confirmed_cum / dplyr::lag(confirmed_cum,k=1)) %>%
dplyr::mutate(active_case_growth = active_cum / dplyr::lag(active_cum,k=1)) %>%
dplyr::mutate(death_case_growth = death_cum / dplyr::lag(death_cum,k=1)) 
plotly::plot_ly(data = df_april) %>%
  plotly::add_trace(
    x = ~date,
    y = ~ total_case_growth - 1,
    type = "scatter",
    mode = "lines+markers",
    name = " Daily Growth Rate of Total Cases",
    line = list(color = active_color),
    marker = list(color = active_color)
  ) %>%
    plotly::add_trace(
    x = ~date,
    y = ~ active_case_growth - 1,
    type = "scatter",
    mode = "lines+markers",
    name = " Daily Growth Rate of Active Cases",
    line = list(color = recovered_color),
    marker = list(color = recovered_color)
  ) %>%
  #  plotly::add_trace(
  #   x = ~date,
  #   y = ~ death_case_growth - 1,
  #   type = "scatter",
  #   mode = "lines+markers",
  #   name = " Daily Growth Rate of Death Cases",
  #   line = list(color = death_color),
  #   marker = list(color = death_color)
  # ) %>%
  plotly::layout(
    title = "",
    legend = list(x = 0.1, y = 0.9),
    yaxis = list(title = "Daily Growth Rate"),
    xaxis = list(title = "Date")
  )
```


Column
-------------------------------------------------------------------------------

### **Country Wise Daily new Cases Smoothened over last 4 days average**

```{r}
daily_confirmed <- coronavirus %>%
  dplyr::filter(type == "confirmed") %>%
  dplyr::filter(as.Date(date) >= "2020-03-06") %>%
  dplyr::mutate(country = country) %>%
  dplyr::group_by(date, country) %>%
  dplyr::summarise(total = sum(cases)) %>%
  dplyr::ungroup() %>%
  tidyr::pivot_wider(names_from = country, values_from = total)

#----------------------------------------
# Plotting the data
col_smoother <- function(col_val){
  abs_col_val<-abs(col_val)
  return((abs_col_val+dplyr::lag(x = abs_col_val,default = 0)+dplyr::lag(x = abs_col_val,n = 2,default = 0)+dplyr::lag(x = abs_col_val,n = 3,default = 0))/4)
}

daily_confirmed %>%
  plotly::plot_ly() %>%
  plotly::add_trace(
    x = ~date,
    y = ~col_smoother(India),
    type = "scatter",
    mode = "lines",
    name = "India"
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~col_smoother(France),
    type = "scatter",
    mode = "lines",
    name = "France"
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~col_smoother(Russia),
    type = "scatter",
    mode = "lines",
    name = "Russia"
  ) %>%
   plotly::add_trace(
    x = ~date,
    y = ~col_smoother(Iran),
    type = "scatter",
    mode = "lines",
    name = "Iran"
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~col_smoother(US),
    type = "scatter",
    mode = "lines",
    name = "US"
  ) %>%
   plotly::add_trace(
    x = ~date,
    y = ~col_smoother(Brazil),
    type = "scatter",
    mode = "lines",
    name = "Brazil"
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~col_smoother(Bangladesh),
    type = "scatter",
    mode = "lines",
    name = "Bangladesh"
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~col_smoother(Germany),
    type = "scatter",
    mode = "lines",
    name = "Germany"
  ) %>%
   plotly::add_trace(
    x = ~date,
    y = ~col_smoother(Italy),
    type = "scatter",
    mode = "lines",
    name = "Italy"
  ) %>%
   
  plotly::add_trace(
    x = ~date,
    y = ~col_smoother(Spain),
    type = "scatter",
    mode = "lines",
    name = "Spain"
  ) %>%
   plotly::add_trace(
    x = ~date,
    y = ~col_smoother(Pakistan),
    type = "scatter",
    mode = "lines",
    name = "Pakistan"
  ) %>%
  plotly::layout(
    title = "",
    legend = list(x = 0.1, y = 0.9),
    yaxis = list(title = "Number of new confirmed cases"),
    xaxis = list(title = "Date"),
    hovermode = "compare",
    margin = list(
      b = 10,
      t = 10,
      pad = 2
    )
  )
```



### **Daily Confirmed Cases raw**
```{r}

#----------------------------------------
# Plotting the data

daily_confirmed %>%
  plotly::plot_ly() %>%
  plotly::add_trace(
    x = ~date,
    y = ~abs(India),
    type = "scatter",
    mode = "lines+markers",
    name = "India"
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~abs(France),
    type = "scatter",
    mode = "lines+markers",
    name = "France"
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~abs(Russia),
    type = "scatter",
    mode = "lines+markers",
    name = "Russia"
  ) %>%
   plotly::add_trace(
    x = ~date,
    y = ~abs(Iran),
    type = "scatter",
    mode = "lines+markers",
    name = "Iran"
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~abs(US),
    type = "scatter",
    mode = "lines+markers",
    name = "US"
  ) %>%
   plotly::add_trace(
    x = ~date,
    y = ~abs(Brazil),
    type = "scatter",
    mode = "lines+markers",
    name = "Brazil"
  ) %>%
    plotly::add_trace(
    x = ~date,
    y = ~abs(Bangladesh),
    type = "scatter",
    mode = "lines+markers",
    name = "Bangladesh"
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~abs(Germany),
    type = "scatter",
    mode = "lines+markers",
    name = "Germany"
  ) %>%
   plotly::add_trace(
    x = ~date,
    y = ~abs(Italy),
    type = "scatter",
    mode = "lines+markers",
    name = "Italy"
  ) %>%
   
  plotly::add_trace(
    x = ~date,
    y = ~abs(Spain),
    type = "scatter",
    mode = "lines+markers",
    name = "Spain"
  ) %>%
   plotly::add_trace(
    x = ~date,
    y = ~abs(Pakistan),
    type = "scatter",
    mode = "lines+markers",
    name = "Pakistan"
  ) %>%
  plotly::layout(
    title = "",
    legend = list(x = 0.1, y = 0.9),
    yaxis = list(title = "Number of new confirmed cases"),
    xaxis = list(title = "Date"),
    hovermode = "compare",
    margin = list(
      b = 10,
      t = 10,
      pad = 2
    )
  )
```

Country Wise
========================================================================================
### **Cases distribution by Country**

```{r daily_summary}
df_EU <- coronavirus %>%
  # dplyr::filter(date == max(date)) %>%
  dplyr::filter(country %in% c("US","Spain","Italy","France","Germany","China","Iran","United Kingdom","Bangladesh","Turkey","Pakistan","Canada","Brazil","Netherlands","Russia",
"Switzerland","Portugal","Austria","Sweden","Finland","India")) %>%
  dplyr::group_by(country, type) %>%
  dplyr::summarise(total = sum(cases)) %>%
  tidyr::pivot_wider(
    names_from = type,
    values_from = total
  ) %>%
  # dplyr::mutate(unrecovered = confirmed - ifelse(is.na(recovered), 0, recovered) - ifelse(is.na(death), 0, death)) %>%
  dplyr::mutate(unrecovered = confirmed - ifelse(is.na(death), 0, death)) %>%
  dplyr::arrange(confirmed) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(country = dplyr::if_else(country == "United Arab Emirates", "UAE", as.character(country))) %>%
  dplyr::mutate(country = dplyr::if_else(country == "Mainland China", "China", country)) %>%
  dplyr::mutate(country = dplyr::if_else(country == "North Macedonia", "N.Macedonia", country)) %>%
  dplyr::mutate(country = trimws(country)) %>%
  dplyr::mutate(country = factor(country, levels = country))

plotly::plot_ly(
  data = df_EU,
  x = ~country,
  # y = ~unrecovered,
  y = ~ confirmed - recovered -death,
  # text =  ~ confirmed,
  # textposition = 'auto',
  type = "bar",
  name = "Active",
  marker = list(color = active_color)
) %>%
  plotly::add_trace(
    y = ~death,
    # text =  ~ death,
    # textposition = 'auto',
    name = "Death",
    marker = list(color = death_color)
  ) %>%
plotly::add_trace(
    y = ~recovered,
    name = "Recovered",
    marker = list(color = recovered_color)
  )%>%
  plotly::layout(
    barmode = "stack",
    yaxis = list(title = "Total cases"),
    xaxis = list(title = ""),
    hovermode = "compare",
    legend = list(x = 0.1, y = 0.9),
    margin = list(
      # l = 60,
      # r = 40,
      b = 10,
      t = 10,
      pad = 2
    )
  )
```


<!-- Map -->
<!-- ======================================================================= -->

<!-- ### **World map of cases** (*use + and - icons to zoom in/out*) -->

<!-- ```{r} -->
<!-- # map tab added by Art Steinmetz -->
<!-- library(leaflet) -->
<!-- #library(leafpop) -->
<!-- library(purrr) -->
<!-- cv_data_for_plot <- coronavirus %>% -->
<!--   # dplyr::filter(country == "India") %>% -->
<!--   dplyr::filter(cases > 0) %>% -->
<!--   dplyr::group_by(country, province, Lat, Long, type) %>% -->
<!--   dplyr::summarise(cases = sum(cases)) %>% -->
<!--   dplyr::mutate(log_cases = 2 * log10(cases)) %>% -->
<!--   dplyr::ungroup() -->
<!-- cv_data_for_plot.split <- cv_data_for_plot %>% split(cv_data_for_plot$type) -->
<!-- pal <- colorFactor(c("orange", "red", "green"), domain = c("confirmed", "death", "recovered")) -->
<!-- map_object <- leaflet() %>% addProviderTiles(providers$Stamen.Toner) -->
<!-- names(cv_data_for_plot.split) %>% -->
<!--   purrr::walk(function(df) { -->
<!--     map_object <<- map_object %>% -->
<!--       addCircleMarkers( -->
<!--         data = cv_data_for_plot.split[[df]], -->
<!--         lng = ~Long, lat = ~Lat, -->
<!--         #                 label=~as.character(cases), -->
<!--         color = ~ pal(type), -->
<!--         stroke = FALSE, -->
<!--         fillOpacity = 0.8, -->
<!--         radius = ~log_cases, -->
<!--         popup = leafpop::popupTable(cv_data_for_plot.split[[df]], -->
<!--           feature.id = FALSE, -->
<!--           row.numbers = FALSE, -->
<!--           zcol = c("type", "cases", "country", "province") -->
<!--         ), -->
<!--         group = df, -->
<!--         #                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F), -->
<!--         labelOptions = labelOptions( -->
<!--           noHide = F, -->
<!--           direction = "auto" -->
<!--         ) -->
<!--       ) -->
<!--   }) -->

<!-- map_object %>% -->
<!--   addLayersControl( -->
<!--     overlayGroups = names(cv_data_for_plot.split), -->
<!--     options = layersControlOptions(collapsed = FALSE) -->
<!--   ) -->
<!-- ``` -->

Summary for US
=======================================================================
```{r}
df_US <- coronavirus %>%
  # dplyr::filter(date == max(date)) %>%
  dplyr::filter(country == "US") %>%
  dplyr::group_by(country, type) %>%
  dplyr::summarise(total = sum(cases)) %>%
  tidyr::pivot_wider(
    names_from = type,
    values_from = total
  ) %>%
  # dplyr::mutate(unrecovered = confirmed - ifelse(is.na(recovered), 0, recovered) - ifelse(is.na(death), 0, death)) %>%
  dplyr::mutate(unrecovered = confirmed - ifelse(is.na(death), 0, death) - ifelse(is.na(recovered), 0, recovered)) %>%
  dplyr::arrange(-confirmed) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(country = dplyr::if_else(country == "United Arab Emirates", "UAE", as.character(country))) %>%
  dplyr::mutate(country = dplyr::if_else(country == "Mainland China", "China", country)) %>%
  dplyr::mutate(country = dplyr::if_else(country == "North Macedonia", "N.Macedonia", country)) %>%
  dplyr::mutate(country = trimws(country)) %>%
  dplyr::mutate(country = factor(country, levels = country))

df_daily_US <- coronavirus %>%
  dplyr::filter(country == "US") %>%
  dplyr::group_by(date, type) %>%
  dplyr::summarise(total = sum(cases, na.rm = TRUE)) %>%
  tidyr::pivot_wider(
    names_from = type,
    values_from = total
  ) %>%
  dplyr::arrange(date) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(active = confirmed - death -recovered) %>%
  dplyr::mutate(
    confirmed_cum = cumsum(confirmed),
    death_cum = cumsum(death),
    recovered_cum = cumsum(recovered),
    active_cum = cumsum(active)
  )

```


Row {data-width=400}
-----------------------------------------------------------------------

### confirmed {.value-box}

```{r}

valueBox(
  value = paste(format(sum(df_US$confirmed), big.mark = ","), "", sep = " "),
  caption = "Total confirmed cases",
  icon = "fas fa-user-md",
  color = confirmed_color
)
```


### active {.value-box}
```{r}
 valueBox( 
   value = paste(format(sum(df_US$unrecovered, na.rm = TRUE), big.mark = ","), " (",
     round(100 * sum(df_US$unrecovered, na.rm = TRUE) / sum(df_US$confirmed), 1),
     "%)",
     sep = "" 
   ),
   caption = "Active cases (% of total cases)", icon = "fas fa-ambulance",
   color = active_color
 ) 
``` 

### death {.value-box}

```{r}

valueBox(
  value = paste(format(sum(df_US$death, na.rm = TRUE), big.mark = ","), " (",
    round(100 * sum(df_US$death, na.rm = TRUE) / sum(df_US$confirmed), 1),
    "%)",
    sep = ""
  ),
  caption = "Death cases (death rate)",
  icon = "fas fa-heart-broken",
  color = death_color
)
```


Row
-----------------------------------------------------------------------

### **Daily cumulative cases by type** (United States only)

```{r}
plotly::plot_ly(data = df_daily_US) %>%
  plotly::add_trace(
    x = ~date,
    # y = ~active_cum,
    y = ~confirmed_cum,
    type = "scatter",
    mode = "lines+markers",
    # name = "Active",
    name = "Confirmed",
    line = list(color = confirmed_color),
    marker = list(color = confirmed_color)
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~ confirmed_cum - recovered_cum - death_cum,
    type = "scatter",
    mode = "lines+markers",
    name = "Active Cases",
    line = list(color = active_color),
    marker = list(color = active_color)
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~ recovered_cum,
    type = "scatter",
    mode = "lines+markers",
    name = "Recovered",
    line = list(color = recovered_color),
    marker = list(color = recovered_color)
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~death_cum,
    type = "scatter",
    mode = "lines+markers",
    name = "Death",
    line = list(color = death_color),
    marker = list(color = death_color)
  ) %>%
  plotly::add_annotations(
    x = as.Date("2020-01-22"),
    y = 1,
    text = paste("First case"),
    xref = "x",
    yref = "y",
    arrowhead = 5,
    arrowhead = 3,
    arrowsize = 1,
    showarrow = TRUE,
    ax = -10,
    ay = -90
  ) %>%
  plotly::add_annotations(
    x = as.Date("2020-02-29"),
    y = 3,
    text = paste("First death"),
    xref = "x",
    yref = "y",
    arrowhead = 5,
    arrowhead = 3,
    arrowsize = 1,
    showarrow = TRUE,
    ax = -90,
    ay = -90
  )  %>%
  plotly::layout(
    title = "",
    yaxis = list(title = "Cumulative number of cases"),
    xaxis = list(title = "Date"),
    legend = list(x = 0.1, y = 0.9),
    hovermode = "compare"
  )
```
Row
-----------------------------------------------------------------------

### **Daily cumulative cases by type Log10 Scale** (United States only)

```{r}
plotly::plot_ly(data = df_daily_US) %>%
  plotly::add_trace(
    x = ~date,
    # y = ~active_cum,
    y = ~log10(confirmed_cum),
    type = "scatter",
    mode = "lines+markers",
    # name = "Active",
    name = "Confirmed",
    line = list(color = confirmed_color),
    marker = list(color = confirmed_color)
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~ log10(confirmed_cum - recovered_cum - death_cum),
    type = "scatter",
    mode = "lines+markers",
    name = "Active Cases",
    line = list(color = active_color),
    marker = list(color = active_color)
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~ log10(recovered_cum),
    type = "scatter",
    mode = "lines+markers",
    name = "Recovered",
    line = list(color = recovered_color),
    marker = list(color = recovered_color)
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~log10(death_cum),
    type = "scatter",
    mode = "lines+markers",
    name = "Death",
    line = list(color = death_color),
    marker = list(color = death_color)
  )  %>%
  plotly::layout(
    title = "",
    yaxis = list(title = "Cumulative number of cases"),
    xaxis = list(title = "Date"),
    legend = list(x = 0.1, y = 0.9),
    hovermode = "compare"
  )
```

India and US Daily stats 
===============================================================================

Column
-------------------------------------------------------------------------------

### **Cases for India**

```{r}

#----------------------------------------
# Plotting the data

df_daily %>% dplyr::filter(as.character(date) > "2020-03-31") %>%
  plotly::plot_ly() %>%
  # plotly::add_trace(
  #   x = ~date,
  #   y = ~confirmed,
  #   type = "scatter",
  #   mode = "lines+markers",
  #   name = "Confirmed"
  # ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~death,
    type = "scatter",
    mode = "lines+markers",
    name = "Death"
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~col_smoother(death),
    type = "scatter",
    mode = "lines",
    name = "Death Rate smoothened"
  ) %>%
  # plotly::add_trace(
  #   x = ~date,
  #   y = ~active,
  #   type = "scatter",
  #   mode = "lines+markers",
  #   name = "Confirmed-Death-Recovered"
  # ) %>%
  #  plotly::add_trace(
  #   x = ~date,
  #   y = ~recovered,
  #   type = "scatter",
  #   mode = "lines+markers",
  #   name = "Recovered"
  # ) %>%
  plotly::layout(
    title = "",
    legend = list(x = 0.1, y = 0.9),
    yaxis = list(title = "Daily new Death cases"),
    xaxis = list(title = "Date"),
    hovermode = "compare",
    margin = list(
      b = 10,
      t = 10,
      pad = 2
    )
  )
```

### **Cases for India smoothened**

```{r}

#----------------------------------------
# Plotting the data

df_daily %>% dplyr::filter(as.character(date) > "2020-03-31") %>%
  plotly::plot_ly() %>%
  plotly::add_trace(
    x = ~date,
    y = ~col_smoother(confirmed),
    type = "scatter",
    mode = "lines+markers",
    name = "Confirmed"
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~col_smoother(death),
    type = "scatter",
    mode = "lines+markers",
    name = "Death"
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~col_smoother(active),
    type = "scatter",
    mode = "lines+markers",
    name = "Confirmed-Death-Recovered"
  ) %>%
   plotly::add_trace(
    x = ~date,
    y = ~col_smoother(recovered),
    type = "scatter",
    mode = "lines+markers",
    name = "Recovered"
  ) %>%
  plotly::layout(
    title = "",
    legend = list(x = 0.1, y = 0.9),
    yaxis = list(title = "Number of Daily new cases smoothened over last 4 days"),
    xaxis = list(title = "Date"),
    hovermode = "compare",
    margin = list(
      b = 10,
      t = 10,
      pad = 2
    )
  )
```

Column
----------------------------------------------------------------------------------

### **Cases for US**

```{r}

#----------------------------------------
# Plotting the data

df_daily_us %>% dplyr::filter(as.character(date) > "2020-03-31") %>%
  plotly::plot_ly() %>%
  # plotly::add_trace(
  #   x = ~date,
  #   y = ~confirmed,
  #   type = "scatter",
  #   mode = "lines+markers",
  #   name = "Confirmed"
  # ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~death,
    type = "scatter",
    mode = "lines+markers",
    name = "Death"
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~col_smoother(death),
    type = "scatter",
    mode = "lines",
    name = "Death Rate smoothened"
  ) %>%
  # plotly::add_trace(
  #   x = ~date,
  #   y = ~active,
  #   type = "scatter",
  #   mode = "lines+markers",
  #   name = "Confirmed-death-Recovered"
  # ) %>%
  #  plotly::add_trace(
  #   x = ~date,
  #   y = ~recovered,
  #   type = "scatter",
  #   mode = "lines+markers",
  #   name = "Recovered"
  # ) %>%
  plotly::layout(
    title = "",
    legend = list(x = 0.1, y = 0.9),
    yaxis = list(title = "Daily new Death cases"),
    xaxis = list(title = "Date"),
    hovermode = "compare",
    margin = list(
      b = 10,
      t = 10,
      pad = 2
    )
  )
```


### **Cases for US smoothened**


```{r}

#----------------------------------------
# Plotting the data US

df_daily_us %>% dplyr::filter(as.character(date) > "2020-03-31") %>%
  plotly::plot_ly() %>%
  plotly::add_trace(
    x = ~date,
    y = ~col_smoother(confirmed),
    type = "scatter",
    mode = "lines+markers",
    name = "Confirmed"
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~col_smoother(death),
    type = "scatter",
    mode = "lines+markers",
    name = "Death"
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~col_smoother(active),
    type = "scatter",
    mode = "lines+markers",
    name = "Confirmed-Death-Recovered"
  ) %>%
   plotly::add_trace(
    x = ~date,
    y = ~col_smoother(recovered),
    type = "scatter",
    mode = "lines+markers",
    name = "Recovered"
  ) %>%
  plotly::layout(
    title = "",
    legend = list(x = 0.1, y = 0.9),
    yaxis = list(title = "Number of Daily new cases smoothened over last 4 days"),
    xaxis = list(title = "Date"),
    hovermode = "compare",
    margin = list(
      b = 10,
      t = 10,
      pad = 2
    )
  )
```

India and US Daily Death Rates 
===============================================================================

Row
-------------------------------------------------------------------------------

### **Cases for India**

```{r}

#----------------------------------------
# Plotting the data

df_daily %>% dplyr::filter(as.character(date) > "2020-03-31") %>%
  plotly::plot_ly() %>%
  plotly::add_trace(
    x = ~date,
    y = ~ col_smoother(death) / col_smoother(confirmed),
    type = "scatter",
    mode = "lines",
    name = "Death Rate (Death/Confirmed for that day) smoothened"
  ) %>%
  plotly::layout(
    title = "",
    legend = list(x = 0.1, y = 0.9),
    yaxis = list(title = "Daily new Death cases"),
    xaxis = list(title = "Date"),
    hovermode = "compare",
    margin = list(
      b = 10,
      t = 10,
      pad = 2
    )
  )
```

Row
-------------------------------------------------------------------------------

### **Cases for US**

```{r}

#----------------------------------------
# Plotting the data

df_daily_us %>% dplyr::filter(as.character(date) > "2020-03-31") %>%
  plotly::plot_ly() %>%
  plotly::add_trace(
    x = ~date,
    y = ~ col_smoother(death) / col_smoother(confirmed),
    type = "scatter",
    mode = "lines",
    name = "Death Rate (Death/Confirmed for that day) smoothened"
  ) %>%
  plotly::layout(
    title = "",
    legend = list(x = 0.1, y = 0.9),
    yaxis = list(title = "Daily new Death cases"),
    xaxis = list(title = "Date"),
    hovermode = "compare",
    margin = list(
      b = 10,
      t = 10,
      pad = 2
    )
  )
```

